---
title: "jdu5sq_HW#3"
author: "Jacqui Unciano"
date: "10/09/2021"
output: html_document
---

Question 1
```{r}
USCovidData<-read.csv("C:\\Users\\jacqu\\Downloads\\School Work\\MathTech Class\\STAT 1601\\DataSets\\USCovid.csv")
```

Question 2
- All variables SANS flip
```{r}
data2a = USCovidData[,1:3]
data2b = USCovidData[,5:6]
Revised.USCovid = data.frame(data2a,data2b)
```

Question 3
- Revised vers descending order in terms of variable cases
```{r}
DCRevised = Revised.USCovid[order(-Revised.USCovid$cases),]
head(DCRevised,8)
```
The state and county with the most cummulative cases is Los Angeles, California.

Question 4
- calculated death rate of county with most cases
```{r}
deathRate = (25263-25245)/2
```

Question 5
- Revised vers descending order in terms of variable deaths
```{r}
DRevised = Revised.USCovid[order(-Revised.USCovid$deaths),]
head(DRevised,8)
```
The state and county with the most deaths is New York City, New York.

Question 6
- calculated death rate of county with most deaths
```{r}
deathRate1 = (33818-33795)/2
```

Question 7
- stats for Virginia
```{r}
VA_Covid = Revised.USCovid[which(Revised.USCovid$state == "Virginia"),]
```

Question 8
- covid cases in descending order for state Virginia
```{r}
DCVA = VA_Covid[order(-VA_Covid$cases),]
head(DCVA,8)
deathRate2 = (1137-1133)/2
```

Question 9
- max deaths in Albemarle and Charlottesville city county
```{r}
ACCCovid = VA_Covid[c(which(VA_Covid$county == "Albemarle"),which(VA_Covid$county == "Charlottesville city")),]
aggregate(ACCCovid[,5],list(ACCCovid$county),max,na.rm=T)
```

