---
title: "jdu5sq_HW#5"
author: "Jacqui Unciano"
date: "23/09/2021"
output: html_document
---

```{r}
library(nycflights13)
library(tidyverse)
library(rvest)
```

Question 1
- average departure delay by carrier, descending order 
```{r}
finalTable = flights %>% group_by(carrier) %>% summarise(Average_delay = mean(dep_delay, na.rm = T)) %>% arrange(desc(Average_delay)) %>% inner_join(airlines, by = "carrier") %>% select(carrier,airline_name = name,Average_delay)
head(finalTable, 6)
```

Question 2
- Hector will have data with larger sd

Question 3
- the IQR of the exam scores after the addition of five points to every exam would stay the same

Question 4
- the median would be larger because Americans love Halloween, so they spends lots of money on the decorations and things like that --> distribution skewed to the left --> the mean is pulled to the left and less than the median

Question 5
- scrapping from IMDb
```{r}
imdbthing = read_html("https://www.imdb.com/search/title/?groups=top_250&sort=user_rating")
title = imdbthing %>% html_nodes(".lister-item-header a") %>% html_text()
rank = imdbthing %>% html_nodes(".text-primary") %>% html_text()
certificate = imdbthing %>% html_nodes(".certificate") %>% html_text()
votes = imdbthing %>% html_nodes(".sort-num_votes-visible span:nth-child(2)") %>% html_text()
rating = imdbthing %>% html_nodes(".ratings-imdb-rating strong") %>% html_text()
runtime = imdbthing %>% html_nodes(".runtime") %>% html_text()
genre = imdbthing %>% html_nodes(".genre") %>% html_text()
top50movies = cbind(title, rank, certificate, votes, rating, runtime, genre)
head(top50movies, 6)
```