---
title: "jdu5sq_HW#10"
author: "Jacqui Unciano"
date: "15/11/2021"
output: html_document
---
```{r}
nba_data = read.csv("C:\\Users\\jacqu\\Downloads\\School Work\\MathTech Class\\STAT 1601\\DataSets\\nba.csv")
library(dplyr)
library(ISLR)
```


Question 1a
- wrangle out all home games, keep away games; W = 1 and L = 0; select MIN, PTS, FG.,X3P.,FT.,REB,STL, AST, TOV,BLK, win
```{r}
away_nba = nba_data %>% mutate(HA=ifelse(grepl("vs", MATCHUP),"home", "away")) %>% filter(HA == "home") %>% mutate(win = ifelse(W.L == "W", 1, 0)) %>% select(MIN, PTS, FG.,X3P.,FT.,REB,STL, AST, TOV,BLK, win)
```

Question 1b
- find LRM for variables: MIN, PTS, FG.,X3P.,FT.,REB,STL, AST, TOV,BLK
- win = -22.32 - 0.05min - 0.01pts + 0.37gf + 0.08x3p + 0.06ft + 0.28reb + 0.34stl - 0.04ast - 0.23tov + 0.14blk
```{r}
away_lrm = glm(win~.,data = away_nba, family = "binomial")
summary(away_lrm)
library(MASS)
lrm_nba = stepAIC(away_lrm,direction = "both", trace = F)
detach("package:MASS")
summary(lrm_nba)
```

Question 1c
- interpret exp coef TOV: for every turn over for the nba team, there is about 20% decrease in the team's odds of winning
```{r}
exp(coef(lrm_nba))
```

Question 1d
- use reasonable values for variables and predict probability of winning using the AIC model
- there is a 74.9% chance that the team will win
```{r}
predict_lrm = data.frame(MIN=100, FG.=38.5, X3P.=3.7, FT.=72.7, REB=16,STL=25,AST=12, TOV=15, BLK=7)
predict(lrm_nba, predict_lrm, type="response")
```
# side note: I know absolutely nothing about basketball(? is this the sport we're looking at?) and I don't really know what the variables stand for, even though I looked at the glossary thing... 

Question 2a
- describe pop and parameter of interest
- population: all NBA games, parameter: the proportion of winning games for NBA away games

Question 2b
- find sample stat of interest
- pop = 1230 where win = 712 (0.5789) and lose = 518 (0.4211)
```{r}
table(away_nba$win)
```


Question 2c
- construct 95% confidence interval for pop proportion
```{r}
prop.test(718, 1230, conf.level = 0.95)
```