---
title: "jdu5sq_HW#8"
author: "Jacqui Unciano"
date: "01/11/2021"
output: html_document
---

```{r}
library(nycflights13)
library(ggplot2)
library(dplyr)
library(ggwordcloud)
library(RColorBrewer)
```

Question 1
- make a polar coor. chart with origin variable
```{r}
ggplot(flights, aes(x=origin))+geom_bar(fill=brewer.pal(3,"Set2"))+coord_polar()
```

Question 2
-create word cloud graph with name, count, and origin
```{r}
dat<-flights%>%
inner_join(airlines, by="carrier")%>%
group_by(name,origin)%>%
summarise(count=n())
ggplot(dat,aes(label=name, size=count, colour=origin))+geom_text_wordcloud_area(rm_outside = TRUE)+scale_size_area(max_size = 50)
```

Question 3
-create tile graph with airline_name, date, and dep_delay
-The grey areas most likely represent when the departure of an airline was mostly eariler than expected (so like "negative" delay times)
```{r}
Thanksgiving_data<-flights%>%
inner_join(airlines, by="carrier")%>%
rename(airline_name=name)%>%
mutate(date=as.Date(time_hour))%>%
filter(date>="2013-11-24" & date<="2013-11-30")
ggplot(Thanksgiving_data,aes(x=date,y=airline_name, fill=dep_delay))+geom_tile(color="white")+scale_fill_distiller(direction = 1)
```

Question 4
-tile graph with airline_name, date, and distance
-the airline that traveled the greatest distance during Thanksgiving week of 2013 is Hawaiian Airlines Inc.
```{r}
ggplot(Thanksgiving_data,aes(x=date,y=airline_name, fill=distance))+geom_tile(color="white")+scale_fill_distiller(palette="RdPu", direction = 1)
```

Question 5
-create Christmas data from Thanksgiving data
```{r}
christmas_data<-flights%>%
inner_join(airlines, by="carrier")%>%
rename(airline_name=name)%>%
mutate(date=as.Date(time_hour))%>%
filter(date>="2013-12-21" & date<="2013-12-31")
Christmas_data = christmas_data%>%group_by(date,origin)%>%summarize(avg_dep_delay=mean(dep_delay, na.rm = TRUE))%>%select(date, origin, avg_dep_delay)
```

Question 6
-create line graph with avg_dep_delay, date, and origin
```{r}
ggplot(Christmas_data,aes(x=date, y=avg_dep_delay,group=origin, color=origin))+geom_line()+geom_point()
```

